---
title: "P8105_hw5_qc2307"
author: "Qixiang Chen"
date: "11/20/2021"
output: github_document
---

```{r}
library(tidyverse)
library(ggplot2)
library(p8105.datasets)
library(patchwork)
library(readxl)
library(httr)
```

```{r}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1
```{r}
homicide_df = 
  read.csv("./untitled folder/homicide-data.csv", na = c("", "Unknown")) %>%
  mutate(
    city_state = str_c(city, state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved"
    )
  ) %>%
  relocate(city_state) %>%
  filter(city_state != "TulsaAL")
```

focus on Baltimore.
```{r}
baltimore_df = 
  homicide_df %>%
  filter(city_state == "BaltimoreMD")

baltimore_summary = 
  baltimore_df %>%
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

baltimore_test = 
  prop.test(
    x = baltimore_summary %>% pull(unsolved),
    n = baltimore_summary %>% pull(n)
  )
baltimore_test %>%
  broom::tidy()
```


```{r}
prop_test_function = function(city_df) {
  
  city_summary = 
    city_df %>%
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n()
    )
  
  city_test = 
    prop.test(
      x = city_summary %>% pull(unsolved),
      n = city_summary %>% pull(n)
    )
  return(city_test)
}

prop_test_function(baltimore_df)

homicide_df %>%
  filter(city_state == "AlbuquerqueNM") %>%
  prop_test_function()
```

Iterate across all cities
```{r}
results_df = 
  homicide_df %>%
  nest(data = uid:resolution) %>%
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>%
  select(city_state, tidy_results) %>%
  unnest(tidy_results) %>%
  select(city_state, estimate, starts_with("conf"))
```


make a plot showing estimates and confidence intervals.
```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```


```{r}
homicide_df %>%
  group_by(city_state) %>%
  summarize(
    unsolved = sum(resolution == "unsolve"),
    n = n()
  ) %>%
  mutate(
    test_results = map2(unsolved, n, prop.test),
    tidy_results = map(test_results, broom::tidy)
  ) %>%
  select(city_state, tidy_results) %>%
  unnest(tidy_results) %>%
  select(city_state, estimate, starts_with("conf"))
```



## Problem 2
#### Step1: create a dataframe containing all files names.
```{r}
file_name = tibble(
  files = list.files("./untitled folder/data")
)
file_name
```


#### Step2: Iterate over file names and read in data for each subject and saving the result as a new variable in the dataframe.
```{r}
dataframe_new = 
  file_name %>%
  mutate(
    data = purrr::map(.x = str_c("./untitled folder/data/", files), ~ read_csv(.x))
    ) %>%
  unnest(data)

dataframe_new
```


#### Step3: Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
```{r}
dataframe_new = 
  dataframe_new %>%
  separate(files, into = c("arm", "subject_id", "csv")) %>%
  select(-csv) %>%
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "observations"
  ) %>%
  mutate(
    arm = recode(arm, "con" = "control", "exp" = "experimental")
  )

dataframe_new
```



#### Step4: Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.
```{r}
spaghetti_plot = 
  dataframe_new %>%
  ggplot(aes(x = week, y = observations, group = subject_id, color = subject_id)) + 
  geom_point(alpha = 0.3) + 
  geom_line() + 
  facet_grid(.~arm) + 
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(
    tittle = "Observations on Each Subject Over Time",
    x = "Week",
    y = "Observation values"
  )

spaghetti_plot
```
Comment: In the two graphs, the graph for control group doesn't have a really clear trend between the independent variable, week, and dependent variable, observation values. In the graph for experimental group, we can observe that there is a generally positive trend between the independent variable, week, and dependent variable, observation values. In this plot, with the increase in week, generally there will be an increase in observation values.


# Problem 3
#### Step1: The code chunk below loads the iris dataset from the tidyverse package
```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species)) %>%
  janitor::clean_names()

iris_with_missing
```

#### Step2: Write a function to serve filling in the missing values
requirement1: For numeric variables, you should fill in missing values with the mean of non-missing values.
requirement2: For character variables, you should fill in missing values with "virginica".
```{r}
filling_table = function(x) {
  if(is.numeric(x)) {
    replace_na(x, mean(x, na.rm = TRUE))
  }
  else if(is.character(x)) {
    x = replace_na(x, "virginica")
  }
}
```


#### Step3: Applying the function
```{r}
iris_with_filled = map(iris_with_missing, filling_table) %>%
  as_tibble()

iris_with_filled
```

